\section{Implementation challenges}

During the whole implementation process we've faced a significant amount of challenges of a diverse nature. For a major part of them we were able to find a feasible solution that was implemented or at least managed to come up with some solution propositions. All the challenges can be split up in the application categories, which a listed below.

\subsection{Organizational challenges}

\begin{enumerate}
  \item Organization of groups
  \begin{itemize}
      \item Problem encountered:\\
      The main problem from the beginning of the practical course was to organize all the project members into equally skilled groups. The splitting principles were also not clear.
      \item Solution found:\\
      The first solution we came up with was to split up into 2 groups of 3 people, which proved efficient enough (or rather the inconveniences didn't show up) at the initial working stages such as acquiring the initial knowledge and getting familiar with the tools. After some time it became clear, that this group separation doesn't work anymore, because the workload of the whole project stretched throughout the remaining time was too much for 3 people to carry out, so it was decided to unite the groups and continue working on the project jointly. This changing of structure mid-project also led to further complications in regards to management within a group, which will be discussed next.
  \end{itemize}
  \item Organization and management within a group
   \begin{itemize}
      \item Problem encountered:\\
        In terms of the management within the group, the major problems that were encountered are: \\
        - Lack of high-level working plan and working structure that everyone can stick to.\\
        - No clear role assignment for the project members, lack of the task management.\\
        - Lack of day-to-day updates and communication.\\
        - No unified repository for everyone to work with and further complications tied with that (follows the problem with groups separation mentioned previously)
      \item Solution found:\\
        The solution that helped to fix (to some degree) first two problems was to (following the unification of 2 groups into one single unit) get rid of the multitasking paradigm  and to assign some specific task or "area of expertise" to each member of the project. Thus, after such decentralization the need for a centralized high-level working plan was decreased, because each participant could organize the working process to fulfill own needs the best. This of course led to deepening the problem of lacking communication and the solution was not the most efficient in terms of implementation speed. 
        The communication problem tied to the absence of a single unified repository for each project member to work with was solved in the second half of the project using GitHub.

  \end{itemize}
\end{enumerate}

\subsection{Software design challenges}
\subsection{PCB design challenges}
\subsection{Casing design challenges}

\textcolor{red}{
Well, here go all the problems we faced coupled with our solutions for them. Potentially the longest part in the report. Can be split in parts similarly to the previous sections (talking about software, board and casing)
}
